\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2016-06-10 paper.tex
New abstract

Human-Robot interaction is an area full of challenges for artificial
intelligence: dynamic, partially unknown environments that are not originally
designed for autonomous machines; a large variety of situations and objects to
deal with, with possibly complex semantics; physical interactions with humans
that requires fine, low-latency control, representation and management of
several mental models, pertinent situation assessment skills...the list goes on.

This article sheds light on some key decisional issues that are to be tackled
for a cognitive robot to share space and tasks with a human, and present our
take on these challenges. We adopt a constructive approach based on the
identification and the effective implementation of individual and collaborative
skills. These cognitive abilities cover geometric reasoning and situation
assessment mainly based on perspective-taking and affordances, management and
exploitation of each agent (human and robot) knowledge in separate cognitive
models, natural multi-modal communication, ``human-aware'' task planning, and human
and robot interleaved plan achievement.

We present our design choices, the articulations between the diverse
deliberative components of the robot, experimental results, and eventually
discuss the strengths and weaknesses of our approach. It appears that
\emph{explicit} knowledge management, both symbolic and geometric, proves to be
key as it pushes for a different, more \emph{semantic} way to address the
decision-making issue in human-robot interactions.

>>>>

Human-Robot Interaction challenges Artificial Intelligence in many regards:
dynamic, partially unknown environments that were not originally designed for
robots; a broad variety of situations with rich semantics to understand and
handle; physical interactions with humans that requires fine, low-latency yet
socially acceptable control strategies; natural and multi-modal communication
which mandates common-sense knowledge and the representation of possibly
divergent mental models. This article attempts to characterize these challenges
and evidences the key decisional issues that need to be addressed for a
cognitive robot to successfully share space and tasks with a human.

We identify in particular the needed individual and collaborative cognitive
skills: geometric reasoning and situation assessment based on perspective-taking
and affordance analysis; acquisition and representation of knowledge models for
multiple interactants (humans and robots); natural multi-modal dialogue;
human-aware task planning; and human-robot joint plan achievement.  The article
discusses each of these abilities (including reference implementations) and show
how they combine in a coherent and original cognitive architecture for
human-robot interaction. Supported by experimental results, we eventually show
how explicit knowledge management, both symbolic and geometric, proves to be
instrumental to richer and more natural human-robot interactions by pushing for
pervasive, human-level semantics within the robot's deliberative system.
